Data for ms. 1

### 2017-05-01 ms1/ms1.Rmd
new model, fig, table

  cc = read_feather(sprintf('../cc_%i.feather', year)) %>%
    mutate(n_cc=rowSums(select_(., '-bene_id')))

@@

  cu = read_tsv('../cu_%i.tsv') %>%
    select(bene_id, n_visits=hospital_op_visits)

@@

```{r single_condition_model}
single_condition_model = function(x, condition) {
  filter(x, age >= 67) %>%
  rename_(.dots=setNames(condition, 'has_condition')) %>%
    glm(n_claims ~ age + is_female + has_condition,
        family=quasipoisson(link='identity'), data=.) %>%
    tidy() %>%
    mutate(condition=condition)
}

single_condition_models = function(bene) {
  lapply(conditions, function(cond) single_condition_model(bene, cond)) %>%
    bind_rows()
}
```

@@

  # then by age group
  # (the input to summarize_by is modified, since we want to group by age *group*,
  # not just by raw age)
  claims_by_age = dat$bene %>%
    bind_rows(. %>% mutate(group='all'),
              . %>% filter(n_cc==0) %>% mutate(group='no_cc'),
              . %>% filter(n_visits==0) %>% mutate(group='no_visits')) %>% 
    group_by(group, age) %>%
    summarize(n_bene=n(),
              mean_n_claims=mean(n_claims),
              sd_n_claims=sd(n_claims),
              mean_n_cc=mean(n_cc),
              sd_n_cc=sd(n_cc),
              mean_n_visits=mean(n_visits),
              sd_n_visits=sd(n_visits)) %>%
    mutate(sem_n_claims=sd_n_claims/sqrt(n_bene),
           sem_n_cc=sd_n_cc/sqrt(n_bene),
           sem_n_visits=sd_n_visits/sqrt(n_bene))

@@

  list(totals=totals,
       claims_by_class=claims_by_class,
       top_abx=top_abx,
       claims_by_sex=claims_by_sex,
       claims_by_race=claims_by_race,
       claims_by_age=claims_by_age,
       chars_by_age_group=chars_by_age_group,
       claims_by_region=claims_by_region,
       chars_by_consumption=chars_by_consumption,
       condition_model=condition_model) %>%
    lapply(function(x) mutate(x, year=year))
}

@@

```{r arrange_data}
data_by_field = function(field) lapply(results, function(x) x[[field]]) %>% bind_rows()

@@

claims_by_race = data_by_field('claims_by_race') %>%
  mutate(cpkp=round(cpkp)) %>%
  spread(year, cpkp) %T>%
  write_tsv('tables/tmp_race.tsv') %>%
  kable

@@

chars_by_consumption = data_by_field('chars_by_consumption') %>%
  mutate_at(vars(`mean age`, `% female`, `mean no. chronic conditions`), function(x) round(x, digits=2)) %>%
  arrange(year, claims_group) %>%
  kable

condition_model_all_years = data_by_field('condition_model') %>%
  left_join(condition_names, by='condition') %>%
  filter(term != '(Intercept)') %>%
  mutate(estimate=round(estimate, digits=3)) %>%
  select(year, condition=condition_name, term, estimate) %T>%
  write_tsv('tables/supptable4_singlecondition.tsv')

condition_model = condition_model_all_years %>%
  filter(year==2011) %>% select(-year) %>%
  spread(term, estimate) %>%
  arrange(desc(has_conditionTRUE)) %T>%
  write_tsv('tables/table3.tsv') %>%
  kable
```

@@

```{r fig1_claims_by_age}
claims_by_age %>%
  filter(year==2011) %>%
  ggplot(aes(x=age,
             y=mean_n_claims,
             ymin=mean_n_claims-sem_n_claims,
             ymax=mean_n_claims+sem_n_claims,
             color=group)) +
  geom_point() +
  geom_linerange() +
  theme_minimal() +
  scale_x_continuous(breaks=c(66, 70, 80, 90, 96))
```

```{r fig1_cc_by_age}
claims_by_age %>%
  filter(year==2011) %>%
  ggplot(aes(x=age,
             y=mean_n_cc,
             ymin=mean_n_cc-sem_n_cc,
             ymax=mean_n_cc+sem_n_cc)) +
  geom_point() +
  geom_errorbar() +
  theme_minimal() +
  scale_x_continuous(breaks=c(66, 70, 80, 90, 100))
```

```{r stratified_claims_by_age}
claims_by_age %>%
  filter(year==2011, between(age, 66, 96)) %>%
  select(age, mean_n_claims, mean_n_claims_0cc) %>%
  gather('group', 'mean_n_claims', mean_n_claims, mean_n_claims_0cc) %>%
  ggplot(aes(x=age,
             y=mean_n_claims,
             color=group,
             group=group)) +
  geom_point(shape=1, cex=5) +
  geom_smooth(method='lm', se=FALSE) +
  theme_minimal(base_size=24) +
  ylab('claims per person') +
  scale_x_continuous(breaks=c(66, 70, 80, 90, 96)) +
  scale_y_continuous(breaks=c(0, 0.5, 1, 1.5, 2.0), limits=c(0, 2))

claims_by_age %>%
  filter(year==2011, between(age, 67, 96)) %>%
  ggplot(aes(x=age, y=mean_n_cc)) +
  geom_point(shape=1, size=6) +
  geom_smooth(method='lm', se=FALSE, col='black') +
  theme_minimal(base_size=24) +
  scale_x_continuous(breaks=c(67, 70, 80, 90, 96)) +
  ylab('mean no. chronic conditions') +
  ylim(0, 6)
```

>>>>

  cc = read_feather(sprintf('../cc_%i.feather', year)) %>%
    select(-ALZH) %>%
    mutate(n_cc=rowSums(select_(., '-bene_id')))

@@

  cu = read_tsv(sprintf('../cu_%i.tsv', year)) %>%
    select(bene_id, n_visits=hospital_op_visits)

@@

```{r single_condition_model}
single_condition_model = function(x, condition_code) {
  filter(x, age >= 67) %>%
  rename_(.dots=setNames(condition_code, 'has_condition')) %>%
    glm(n_claims ~ age + is_female + has_condition + n_visits,
        family=quasipoisson(link='identity'), data=.) %>%
    tidy() %>%
    mutate(condition=condition_code)
}

single_condition_models = function(bene) {
  lapply(conditions, function(cond) single_condition_model(bene, cond)) %>%
    bind_rows()
}

all_condition_model = function(bene) {
  f = formula(paste0('n_claims ~ age + is_female + n_visits + ', paste0(conditions, collapse=' + ')))
  start = rep(0.1, length(all.vars(f)))
  filter(bene, age >= 67) %>%
    glm(f, family=quasipoisson(link='identity'), start=start, data=.) %>%
    tidy
}

```

@@

  # then by age group
  # (the input to summarize_by is modified, since we want to group by age *group*,
  # not just by raw age)
  claims_by_age = dat$bene %>%
    mutate(group='all') %>%
    bind_rows(filter(., n_cc==0) %>% mutate(group='no_cc'),
              filter(., n_visits==0) %>% mutate(group='no_visits')) %>% 
    group_by(group, age) %>%
    summarize(n_bene=n(),
              mean_n_claims=mean(n_claims),
              sd_n_claims=sd(n_claims),
              mean_n_cc=mean(n_cc),
              sd_n_cc=sd(n_cc),
              mean_n_visits=mean(n_visits),
              sd_n_visits=sd(n_visits)) %>%
    mutate(sem_n_claims=sd_n_claims/sqrt(n_bene),
           sem_n_cc=sd_n_cc/sqrt(n_bene),
           sem_n_visits=sd_n_visits/sqrt(n_bene))

@@

  big_model = all_condition_model(dat$bene)

  list(totals=totals,
       claims_by_class=claims_by_class,
       top_abx=top_abx,
       claims_by_sex=claims_by_sex,
       claims_by_race=claims_by_race,
       claims_by_age=claims_by_age,
       chars_by_age_group=chars_by_age_group,
       claims_by_region=claims_by_region,
       chars_by_consumption=chars_by_consumption,
       condition_model=condition_model,
       big_model=big_model) %>%
    lapply(function(x) mutate(x, year=year))
}

@@

```{r arrange_data1}
data_by_field = function(field) lapply(results, function(x) x[[field]]) %>% bind_rows()

@@

claims_by_race = data_by_field('claims_by_race') %>%
  mutate(cpkp=round(cpkp)) %>%
  spread(year, cpkp) %>%
  arrange(desc(`2011`)) %T>%
  write_tsv('tables/tmp_race.tsv') %>%
  kable

@@

chars_by_consumption = data_by_field('chars_by_consumption') %>%
  mutate_at(vars(`mean age`, `% female`, `mean no. chronic conditions`), function(x) round(x, digits=2)) %>%
  arrange(year, claims_group) %>%
  kable
```

```{r arrange_data2}
condition_model_all_years = data_by_field('condition_model') %>%
  left_join(condition_names, by='condition') %>%
  filter(term != '(Intercept)') %>%
  mutate(estimate=round(estimate, digits=3)) %>%
  select(year, condition=condition_name, term, estimate) %T>%
  write_tsv('tables/supptable4_singlecondition.tsv')

condition_model = condition_model_all_years %>%
  filter(year==2011) %>% select(-year) %>%
  spread(term, estimate) %>%
  arrange(desc(has_conditionTRUE)) %T>%
  write_tsv('tables/table3.tsv') %>%
  kable

big_model = data_by_field('big_model') %>%
  mutate(term=stringr::str_replace(term, 'TRUE$', '')) %>%
  left_join(rename(condition_names, term=condition, condition=condition_name), by='term') %>%
  filter(term != '(Intercept)') %>%
  mutate(term=if_else(is.na(condition), term, condition)) %>%
  select(year, term, estimate, std.error) %T>%
  write_tsv('tables/tmp_big_model.tsv')
```

@@

```{r fig1_claims_by_age}
# Show three lines: claims among all beneficiaries, among those with no ccs,
# and those with no OP visits. Exclude the no_cc, age=66 datapoint, which is
# artificially high.
claims_by_age %>%
  filter(year==2011, !(group=='no_cc' & age < 67)) %>%
  ggplot(aes(x=age,
             y=mean_n_claims,
             ymin=mean_n_claims-sem_n_claims,
             ymax=mean_n_claims+sem_n_claims,
             color=group)) +
  geom_point() +
  geom_linerange() +
  theme_minimal() +
  scale_x_continuous(breaks=c(66, 70, 80, 90, 96))
```

```{r fig1_cc_by_age}
claims_by_age %>%
  filter(year==2011, age >= 67) %>%
  ggplot(aes(x=age,
             y=mean_n_cc,
             ymin=mean_n_cc-sem_n_cc,
             ymax=mean_n_cc+sem_n_cc)) +
  geom_point() +
  geom_linerange() +
  theme_minimal() +
  scale_x_continuous(breaks=c(67, 70, 80, 90, 96)) +
  ylim(0, 6)
```

```{r visits_by_age}
claims_by_age %>%
  filter(year==2011) %>%
  ggplot(aes(x=age,
             y=mean_n_visits,
             ymin=mean_n_visits-sem_n_visits,
             ymax=mean_n_visits+sem_n_visits)) +
  geom_point() +
  geom_linerange() +
  theme_minimal() +
  scale_x_continuous(breaks=c(66, 70, 80, 90, 96))
```
